%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Head Of Operations} % Job title
    {dentalessence} % Organisation
    {Sussex/Surrey, UK} % Location
    {2019 - 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led implementation of digital compliance system, simplifying processes and driving cross-functional collaboration, drastically decreasing compliance workload.}
        \item {Pioneered the integration of VOIP, carefully selecting and honing down a variety of providers to just one, reducing service costs dramatically whilst also collaborating on a custom automation solution to make our phone experience even easier for our employees and seamless for our patients.}
        \item {Initiated the adoption of a cloud-based practice management solution to eliminate the need for physical infrastructure in our practices and allow for seamless practice collaboration across the board}
        \item {\textbf{Technical Skills:} TCP/IP, VOIP, Cloud Concepts, Windows Server, Dental Imaging (DICOM).}
        \item {\textbf{Soft Skills:} Negotiation, Problem-solving, Communication, Attention to Detail, Adaptability.}
      \end{cvitems}
    }

  \cventry
    {IT Consultant} % Job title
    {dentalessence} % Organisation
    {Sussex/Surrey, UK} % Location
    {2018 - 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Single-handedly provided effective and dependable company-wide IT support}.
        \item {Orchestrated and executed the transition of network infrastructure, dramatically improving security and site reliability.}
        \item {Facilitated the adoption of digital forms across multiple practices by deploying iPads and wireless
infrastructure, seamlessly integrating them with proprietary software.}
        \item {Rapidly acquired expertise in proprietary and low documentation dental software, providing effective and timely support.}
        \item{Pioneered various automation solutions, proactively identifying and addressing issues before they
impacted staff, including the prevention of critical network outages caused by third-party providers.}
        \item {\textbf{Technical Skills:} TCP/IP, VOIP, Cloud Concepts, Windows Server, Dental Imaging (DICOM), Network Infrastructure.}
        \item {\textbf{Soft Skills} Problem-solving, Communication, Attention to Detail, Adaptability, Continuous Learning.}
      \end{cvitems}
    }


  \cventry
    {Specialist} % Job title
    {Apple} % Organisation
    {Brighton, UK} % Location
    {2012 - 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided exceptional and thoughtful customer experiences}
        \item {Hosted in-store training sessions on topics such as apps within the Apple ecosystem and how to navigate Apple devices.}
        \item {Rapidly learnt about new products and services.}
        \item {\textbf{Technical Skills:} MacOS, iOS, iPadOS.}
        \item {\textbf{Soft Skills:} Communication, Adaptability, Problem-solving, Presentation Skills.\\}
        \smallskip
      \end{cvitems}
    }


\end{cventries}
