%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Group Project} % Organisation
    {\href{https://github.com/NDR-114/bowie-bnb-project}{Bowie BNB}} % Project
    {Online, UK} % Location
    {September 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Designed and implemented a full stack web application using Python, Flask, Jinja2, PostgreSQL, Tailwind CSS and Flowbite.}
        \item {Collaborated and created a relational database with PostgreSQL to manage dynamic data such as listing and bookings.}
        \item {Helped create a visually appealing and responsive user interface with Tailwind CSS and Flowbite, demonstrating attention to user experience.}
        \item {\textbf{Technical Skills:} Python, Flask, PostgreSQL, PyTest, Git, GitHub, CSS, Tailwind CSS, Flowbite.}
        \item {\textbf{Soft Skills:} Teamwork, Logical Thinking, Creativity, Adaptability, Attention to Detail, Problem-solving.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry % Organisation
    {Personal Project}
    {\href{https://github.com/NDR-114/fence_calculator}{Fence Calculator}}% Project
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Developed a C program to calculate materials required for the fence I was constructing for my home, in an effort to demonstrate my learning of the C Language.}
        \item {Designed algorithms to compute quantities of feather edge boards, posts and other components based on user-specified measurements.}
        \item {Created a basic command-line interface in order for the user to input their information.}
        \item {\textbf{Technical Skills:} C, Git, GitHub.}
        \item {\textbf{Soft Skills:} Logical Thinking, Problem-solving, Creativity.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  % Organisation
    {Personal Project}
    {\href{https://github.com/NDR-114/a-quote-a-day}{'A Quote a Day'}}% Project
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Developed a basic random quote viewing application using Next.js and React.}
        \item {Implemented API integration from a public API and used tools such as Postman to understand how
the API was configured.}
        \item {Utilised CSS, Tailwind CSS and Flowbite components to provide a beautiful and easy to navigate
user experience.}
        \item {Developed a basic understanding of React Hooks and utilised this knowledge to provide features
such as refresh functionality.}
        \item {\textbf{Technical Skills:} Javascript, React, Next.js, CSS, Tailwind CSS, REST API Integration, Postman}
        \item {\textbf{Soft Skills:} Creativity, Attention to Detail, Problem-solving, User-centric Design.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
